### 2016-05-19 w-wires/paper_gerasimovda.tex
Cleanup, numerical estimations reflecting calculation in the paper

\DeclarePairedDelimiter{\abs}{\lvert}{\rvert}

@@

We'll use the inequality:

\[
\frac{x}{1 + x} \le \ln(1 + x)
\]
, which holds for $-1 < x \le 0$. % As $x$ goes to $-1$,

We'll rewrite it in a more convenient form by a substitution $x \to s(k) - 1$:

\[
1 - \frac{1}{s(k)} \le \ln s(k)
\]

Since $s(k)$

@@

We know that $s(k)$ is bounded by $1$ from above in the upper complex plane  ($\Im k \ge 0$) \todo{why?}, hence $\ln \abs{\det S} \le 0$.

Outline of the following steps: we compute a lower bound $l(k)$ for $s(k)$, such that $0 \le l(k) \le s(k)$, and we prove that $\int \ln l(k)$ converges. Since $\ln l(k) \le \ln s(k)$, that will prove convergence of the original integral.

@@

$s_3(k)$ helps us to deal

@@

>>>>

% \DeclarePairedDelimiter{\abs}{\lvert}{\rvert}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\norm}[1]{\left\lVert #1 \right\rVert}
% \DeclarePairedDelimiterX{\norm}[1]{\lVert}{\rVert}{#1}

@@

% We'll use the inequality:

% \[
% \frac{x}{1 + x} \le \ln(1 + x)
% \]
% , which holds for $-1 < x \le 0$. % As $x$ goes to $-1$,

% We'll rewrite it in a more convenient form by a substitution $x \to s(k) - 1$:

% \[
% 1 - \frac{1}{s(k)} \le \ln s(k)
% \]

% Since $s(k)$

@@

We know that $s(k)$ is bounded by $1$ from above in the upper complex plane  ($\Im k \ge 0$) \todo{why?}, hence $\ln \abs{\det S} \le 0$ and the desired integral is bounded from above by $0$. However, we have to show that the integral is bounded from below as well. So, next, we will compute a lower bound $l(k)$ for $s(k)$, such that $0 \le l(k) \le s(k)$, and will prove that $\int \ln l(k)$ converges to $0$. Since $\ln l(k) \le \ln s(k)$, that will prove convergence of the original integral.

@@

\todo{We might need one more estimate to ensure $l(x + 0 \iu) = 1$}

@@

\todo{Use Schwartz inequality????}

\subsection*{Proof of convergence}

\[
l(k) =
\begin{cases}
1 \\
2 \\
3 
\end{cases}
\]

Not than we have an estimate for $s(k)$ on the whole upper complex plane, we can compute the lower bound for the original integral. For fixed $r$ (radius of the contour in Cayley space), the integral looks like:

\[
\int\limits_{C_r} \ln l(k) \frac{1}{(k + i)^2} dk
\]

, where $C_r$ is the image of the curve $\abs{\zeta} = r$ under the inverse Cayley transform.

\todo{Calculate C(r) and R(r)}

Substituting $k \to R \eexp{\iu t} + \iu C$, we get:

\todo{multiply by $2 \iu$ due to derivative of Cayley transform}

\[
\int\limits_{0}^{2 \pi} \ln l(R \eexp{\iu t} + \iu C) \frac{1}{(R \eexp{\iu t} + \iu C + i)^2} R \iu dt
\]

To estimate this integral, we'll use Cauchy-Schwartz inequality:

\[
\big| \langle u,v \rangle \big| \leq \left\|u\right\| \left\|v\right\|
\]

, or, to be more specific, its $\mcL^2[a, b]$ version:

\[
\abs{
\int\limits_{t=a}^{b} f(t) g^*(t) dt
}^2
\le
\int\limits_{t=a}^b \abs{f(t)}^2 dt 
\int\limits_{t=a}^b \abs{g(t)}^2 dt 
\]

To make use of the inequality, we take

\todo{CONJUGATE!!!}
\begin{align*}
a    &= 0 \\
b    &= 2 \pi \\
f(t) &= \ln l(R \eexp{\iu t} + \iu C) \frac{\sqrt{R}}{R \eexp{\iu t} + \iu C + i} \\
g(t) &= \iu \frac{\sqrt{R}}{R \eexp{\iu t} + \iu C + i}
\end{align*}

\todo{Integral of $g(t)$ is estimated by $\pi$}
